Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-05-05 cav2017/cav2017.tex
Small spelling correction
Used American English instead of British.
Added AE badge
Added the AE .pdf and command.

@@

\textit{Benchmark selection:} We report an assessment of both our approaches
over a diverse set of real-world benchmarks.  Nevertheless, this set of
benchmarks is limited within the scope of this paper and the performance may
not generalize to other benchmarks.\\
%
\textit{Plant precision and discretization heuristics:} Our algorithm to
select suitable FWL word widths to model the plant behavior %% employs a
%% heuristic based on user-provided controller word-width specifications.
increases the precision by 8 bits at each step 
in order to be compliant with the CBMC type API. %% , we increase the precision
%% by 8 bits at each step.
Similarly, for discretization, we run multiple discretisations for each
benchmark and retain the fastest run.
%% where we may need to increase the precision of the time
%% discretization,
%% we select the time steps for the discretizations on a
%% similar basis.
This works sufficiently well for our benchmarks, but
performance may suffer in some cases, for example if the completeness
threshold is high.\\
%
\textit{Abstraction on other properties:} The performance gain from abstract
acceleration may not hold for more complex properties than safety, for
instance ``eventually reach and always remain in a given safe set''.

>>>>

\usepackage[firstpage]{draftwatermark}\SetWatermarkText{\hspace*{5.2in}\raisebox{5in}{\includegraphics[scale=0.1]{aec-badge-cav}}}\SetWatermarkAngle{0}

@@

\textit{Benchmark selection:} We report an assessment of both our approaches
over a diverse set of real-world benchmarks.  Nevertheless, this set of
benchmarks is limited within the scope of this paper and the performance may
not generalize to other benchmarks.\\
%
\textit{Plant precision and discretization heuristics:} Our algorithm to
select suitable FWL word widths to model the plant behavior %% employs a
%% heuristic based on user-provided controller word-width specifications.
increases the precision by 8 bits at each step 
in order to be compliant with the CBMC type API. %% , we increase the precision
%% by 8 bits at each step.
Similarly, for discretization, we run multiple discretizations for each
benchmark and retain the fastest run.
%% where we may need to increase the precision of the time
%% discretization,
%% we select the time steps for the discretizations on a
%% similar basis.
This works sufficiently well for our benchmarks, but
performance may suffer in some cases, for example if the completeness
threshold is high.\\
%
\textit{Abstraction on other properties:} The performance gain from abstract
acceleration may not hold for more complex properties than safety, for
instance ``eventually reach and always remain in a given safe set''.
